Women in Kenya Severely Lack Knowledge on Source of Condom Supply Across All Age Groups And Provinces

### 2022-04-04 outputs/paper/paper.Rmd
updated Introduction section and title of paper.Rmd.

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Tian Yi Zhang
thanks: "Code and data supporting this paper are available at: AOIWDJAWOIDJ"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point).

@@

>>>>

---
title: "Women in Kenya Severely Lack Knowledge on Source of Condom Supply Across All Age Groups And Provinces"
subtitle: "My subtitle if needed"
author: 
  - Tian Yi Zhang
thanks: "Code and data supporting this paper are available at: AOIWDJAWOIDJ"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

The remainder of this paper contains analysis on the dataset and the resulting
findings. Section \@ref(data) details the data analysis of this paper. Section
\@ref(raw-data-origin-and-dhs-methodology) discusses the origin of the raw
data used in this paper, and \@ref(dataset-parsing-and-cleaning) details
the extraction process for the dataset. Section \@ref(results) details the
findings from the data analysis, and all limitations and potential extensions
are discussed in Section \@ref(discussion).

@@

The graphs in the Data section have demonstrated that a significantly higher
percentage of women in Kenya have no knowledge on a source to obtain condoms;
the difference in percentage ranges from 28.8% to 12.2% depending on the
age group, and on average, the difference in percentage of women and men
who have no konwledge on a source to obtain condoms is 15.1%.
